### 2019-12-03 monograph/chapters/conclusion.tex
Detached the main conclusion block from the first \lang command

\begin{enumerate}[leftmargin=*]
    \item
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter};
    \item
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented;
    \item
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings \cite{universalIndentGUI};
    \item
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
\end{enumerate}
}{%
    Neste trabalho foi proposta uma implementação de um algoritmo que trabalha diretamente com a Árvore Sintática da gramática do programa de entrada (\fullref{software_implementation}).
    Apesar de simples,
    esta implementação é o primeiro passo para criação de novos formatadores de código~=fonte.
    Servindo de base para criação de novos algoritmos voltados a utilizar Árvore Sintática da gramática da linguagem,
    ao contrário da Árvore Sintática do programa de entrada.

@@

    Em um modelo de trabalho onde se faz a formatação do código~=fonte diretamente com a Árvore Sintática do programa de entrada,
    é possível realizar verificações da semântica do programa que está sendo formatado com maior facilmente,
    pelo acesso direto a Árvore Sintática do programa de entrada,
    (base para Análise Semântica (\fullref{analiseSemantica})).
    Por isso,
    os algoritmos de formatação de código~=fonte desenvolvidos para este trabalho também irão precisar considerar os aspectos semânticos.
    Entretanto,
    estes algoritmos terão uma dificuldade adicional.
    Enquanto os algoritmos de Análise Semântica trabalham com base na Árvore Sintática do programa de entrada,
    os algoritmos de Análise Semântica deste trabalho precisam trabalhar com base na Árvore Sintática da gramática do programa de entrada.
    O que levará a necessidade da criação de novos algoritmos de Análise Semântica capazes de trabalhar com a Árvore Sintática da gramática do programa de entrada.
}

>>>>

\begin{enumerate}[leftmargin=*]
    \item
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter};
    \item
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented;
    \item
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings \cite{universalIndentGUI};
    \item
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
\end{enumerate}
}{}

Neste trabalho foi proposta uma implementação de um algoritmo que trabalha diretamente com a Árvore Sintática da gramática do programa de entrada (\fullref{software_implementation}).
Apesar de simples,
esta implementação é o primeiro passo para criação de novos formatadores de código~=fonte.
Servindo de base para criação de novos algoritmos voltados a utilizar Árvore Sintática da gramática da linguagem,
ao contrário da Árvore Sintática do programa de entrada.

@@

Em um modelo de trabalho onde se faz a formatação do código~=fonte diretamente com a Árvore Sintática do programa de entrada,
é possível realizar verificações da semântica do programa que está sendo formatado com maior facilmente,
pelo acesso direto a Árvore Sintática do programa de entrada,
(base para Análise Semântica (\fullref{analiseSemantica})).
Por isso,
os algoritmos de formatação de código~=fonte desenvolvidos para este trabalho também irão precisar considerar os aspectos semânticos.
Entretanto,
estes algoritmos terão uma dificuldade adicional.
Enquanto os algoritmos de Análise Semântica trabalham com base na Árvore Sintática do programa de entrada,
os algoritmos de Análise Semântica deste trabalho precisam trabalhar com base na Árvore Sintática da gramática do programa de entrada.
O que levará a necessidade da criação de novos algoritmos de Análise Semântica capazes de trabalhar com a Árvore Sintática da gramática do programa de entrada.
